Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-16 parallel.tex
Edits to introduction (also adding section labels to some other files).
Adding strong scaling figures to the text.

\section{Parallel Strategy and Performance}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/enzo_unigrid_weak_scaling.eps}
\caption{\enzo\ weak scaling performance for a set of Lyman alpha
forest cosmology simulations with constant comoving spatial resolution
per grid cell, showing cell updates per second per computational core
plotted as a function of the number of root grid tiles of dimension
$128^3$ (R) in each dimension.  The number of MPI tasks is N$ = R^3$,
so R$ = 16$ on this plot corresponds to a $2048^3$ computational mesh
running on 4096 MPI tasks.  This plot goes from R$ = 2$ (8 MPI tasks)
to R$ = 24$ (13,824 MPI tasks) on two supercomputers -- NICS Kraken
and ORNL Jaguar when they were Cray XT4 systems -- and using 1, 2 or 4
MPI processes per node, where each compute node contained a single
quad-core AMD Opteron CPU having a speed of 2.1 GHz on Jaguar and 2.3
GHz on Kraken.}
\label{fig.uniscale}
\end{center}
\end{figure}

\subsubsection{AMR scaling \red{(Greg)}}

>>>>

\section{Parallel Strategy and Performance}
\label{sec.parallel}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/enzo_unigrid_weak_scaling.eps}
\caption{\enzo\ weak scaling performance for a set of Lyman alpha
forest cosmology simulations with constant comoving spatial resolution
per grid cell, showing cell updates per second per computational core
plotted as a function of the number of root grid tiles of dimension
$128^3$ (R) in each dimension.  The number of MPI tasks is N$ = R^3$,
so R$ = 16$ on this plot corresponds to a $2048^3$ computational mesh
running on 4096 MPI tasks.  This plot goes from R$ = 2$ (8 MPI tasks)
to R$ = 24$ (13,824 MPI tasks) on two supercomputers -- NICS Kraken
and ORNL Jaguar when they were Cray XT4 systems -- and using 1, 2 or 4
MPI processes per node, where each compute node contained a single
quad-core AMD Opteron CPU having a speed of 2.1 GHz on Jaguar and 2.3
GHz on Kraken.}
\label{fig.uniscale}
\end{center}
\end{figure}

@@

\subsubsection{AMR scaling \red{(John)}}

\begin{figure}
\begin{center}
\includegraphics[width=0.48\textwidth]{figures/strong_scaling_levels.eps}
\hfill
\includegraphics[width=0.48\textwidth]{figures/strong_scaling_routines.eps}
\end{center}
\caption{\emph{Left:} Strong scaling test of a 512$^3$ AMR
  cosmological calculation.  The root grid scaling is not
  representative of the true strong scaling of Enzo because the root
  grid tiles are not repartitioned when a simulation is restarted with
  additional cores.  The weak scaling test in Figure
  \ref{fig.uniscale} is more representative of the scaling on the root
  level.  The performance in the refined levels show good strong
  scaling up to 4096 cores.  \emph{Right:} Time spent in the major
  routines in the same AMR calculation.}
\label{fig:amr_hierarchy}
\end{figure}
